---
title: "WUP_04"
author: "Giselle Alvarez!"
date: "Spring 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
GSSdata <- read.csv(file="GSScsv.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
  
```{r}
barchartGC(~BIGBANG + POSTLIFE,data=GSSdata)
barchartGC(~BIGBANG + POSTLIFE,data=GSSdata, type="percent")

```
```{r}
dd2 <- GSSdata %>% group_by(BIGBANG,POSTLIFE) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))

basicC <- ggplot(dd2,aes(x=BIGBANG,y=count,fill=POSTLIFE))
basicC + geom_bar(stat="identity",position="dodge")
#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=BIGBANG,y=prcnt*100,fill=POSTLIFE)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```  
  
Th barchart  shows that people that believe in the BIGBANG theory are less likely to beleive in the postlife.
   
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
#### Using ggplot

```{r}
basicCN <- ggplot(GSSdata,aes(x=DEGREE,y=WORDSUM))

basicCN + geom_boxplot()
```
  
From the graph it looks like graduate does better then LT High School and high school.
    
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
```{r}
table1 <- xtabs(~BIGBANG + POSTLIFE, data=GSSdata)
rowPerc(table1)
colPerc(table1)
```
  
LT high school is the littlest, followed by high school, bachelor, junior college, with Graduate at its best.
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
  
```{r}
model1 <- aov(WORDSUM~DEGREE,data=GSSdata)
summary.aov(model1)
```
  
```{r}
par(mar = c(3, 13.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```
  
LT high school and graduate are different and highschool and graduate are different.
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
Yes there is a difference in WORDSUM test performance, graduate students did better then LT high school junior students 
  